---
title: "Project-Final"
author: "Nihal Biswas"
date: "2023-06-10"
output: html_document
---

# Exporting Data

```{r}
library(readxl)
setwd("C:\\Users\\Admin\\Desktop\\college\\project")
electric=read_excel("Compiled.xlsx",sheet = "Sheet2")
electric=electric[,-2:-3]
electric_only=na.omit(electric[,1:5])
head(electric)
```



# FORECASTING URBAN POPULATION TILL 2050

```{r}
library(tseries)
library(forecast)
library(urca)
adf.test(electric$Urban_Population)
```

- P value greater than 0.05, hence the data is not stationary.
- We thus the ACF value to see the optimum number of lags at which the data becomes stationary.


```{r}
acf(electric$Urban_Population)
```

- From the graph we can see that the optimal number of lags is 5.
- We now check for stationary of the variables at lag 5.

```{r}
Urbanpop_lag = diff(electric$Urban_Population,lag = 15)
adf.test(Urbanpop_lag)
```

- Hence we can conclude that the data is stationary at lag of order 15.


## ARIMA model to forecast


```{r}
Urbanpop_ARIMA = auto.arima(electric$Urban_Population,ic = "aic")
summary(Urbanpop_ARIMA)
checkresiduals(Urbanpop_ARIMA)
Urbanpop_forecasted = forecast(Urbanpop_ARIMA,h = 2050 - electric$YEAR[nrow(electric)])
plot(Urbanpop_forecasted)
Urbanpop_forecasted = as.data.frame(Urbanpop_forecasted)
Urbanpop_forecasted
```

- We see that the residuals have a normal distribution, thus we move forward with the forecasting.


# FORECASTING THE NUMBER OF INDUSTRIES TILL 2050

```{r}
Industries = na.omit(electric$`Total Industries`)
adf.test(Industries)
```

- We see that the original data is not stationary, hence we look at the ACF graph to determine the optimal number of lags at which the data will be stationary.


```{r}
acf(Industries)
```

- Here we can see that the data will be stationary at lag of order 4.
- We shall confirm this through the Augmented Dicky-Fueller test.


```{r}
Industries_lag = diff(Industries,lag = 4)
adf.test(Industries_lag)
```

- We can observe that the data is not stationary at lag 4 also. Hence, we check at lag 3 and 2 and make conclusions accordingly.

```{r}
Industries_lag1 = diff(Industries,lag = 3)
adf.test(Industries_lag1)
Industries_lag2 = diff(Industries,lag = 2)
adf.test(Industries_lag2)
```

- Hence we see that the test is closer to significance at lag 3 than at lag 2 or 4.
- Hence we move forward with lag of order 3.


## ARIMA modelling

```{r}
Industries_ARIMA = auto.arima(Industries,ic = "aic")
summary(Industries_ARIMA)
checkresiduals(Industries_ARIMA)
Industries_forecasted = forecast(Industries_ARIMA, h = 36)
plot(Industries_forecasted)
Industries_forecasted=as.data.frame(Industries_forecasted)
Industries_forecasted
```


# Data Cleaning

```{r}
electric_omitted=na.omit(electric)
head(electric_omitted)
```

# Finding the type of relationship  

```{r}
library(ggplot2)
ggplot(electric_omitted,aes(Urban_Population,`Electric_power_consumption_(kWh_per_capita)`))+geom_point()+geom_smooth(method = "lm",se=F)
```



# Linear Regression Model 


```{r}
## Level-Level Model
model.01=lm(electric_only$`Electric_power_consumption_(kWh_per_capita)`~electric_only$Urban_Population)

## Level-log Model
model.02=lm(electric_only$`Electric_power_consumption_(kWh_per_capita)`~log(electric_only$Urban_Population))
model.03=lm(log(electric_only$`Electric_power_consumption_(kWh_per_capita)`)~electric_only$Urban_Population)

## Log- Log model
model.04=lm(log(electric_only$`Electric_power_consumption_(kWh_per_capita)`)~log(electric_only$Urban_Population))

# Quadratic
model.05=lm(log(electric_only$`Electric_power_consumption_(kWh_per_capita)`)~I(electric_only$Urban_Population^2))

library(stargazer)
stargazer(model.01,model.02,model.03,model.04,model.05,type = "text")
```


Electric_power_consumption regressed over %_of_Urban_population_from_total_population


# Auto-correlation

```{r}
acf(model.01$residuals)
acf(model.02$residuals)
acf(model.03$residuals)
acf(model.04$residuals)
acf(model.05$residuals)
```

## Auto-correlation Test

```{r}
library(lmtest)
bgtest(model.01,order=3,type="Chisq")
bgtest(model.02,order=3,type="Chisq")
bgtest(model.03,order=3,type="Chisq")
bgtest(model.04,order=3,type="Chisq")
bgtest(model.05,order=3,type="Chisq")
```

- All the above models contains auto-correlation of order3.
- The quadratic Form has the highest R-squared value.


# Model 4

```{r}
sqr_Urban_Population=electric_omitted$Urban_Population*electric_omitted$Urban_Population
model4=lm(electric_omitted$`Electric_power_consumption_(kWh_per_capita)`~sqr_Urban_Population)
summary(model4)
```

- The model 4 shows a positive intercept, which is statistically significant. 
- However in the residual plot it shows a pattern in the later half of the graph. There is some problem with our model. However model 4 is theoretically closest model and we shall build more upon that.

```{r}
plot(model4)
```


# Cleaning Model 4

Adding the number of industries to dampen the effect of heteroscedasticity

```{r}
model4.1=lm(electric_omitted$`Electric_power_consumption_(kWh_per_capita)`~sqr_Urban_Population+electric_omitted$`Total Industries`)
summary(model4.1)
stargazer(model4.1,type = "text")
```

- using model 4 even though the pattern in the residual plot is dampened and the residual is not showing a prominent pattern. However, the intercept in this case again becomes negative which is not in lined with our common knowledge. 
- We can also see that by adding the Total Industries variable the adjusted R-squared value also increased.

# We have to perform wald f test in model 4 and model 4.1

```{r}

```


```{r}
acf(model4.1$residuals)
bgtest(model4.1,order=3,type="Chisq")
```

- After addition of new variable the residuals are also not correlated any more.


# Visualizing with our estimated values

```{r}
predict(model4.1,electric_omitted)
electric_omitted$Estimated_values=predict(model4.1,electric_omitted)
ggplot(electric_omitted,aes(Urban_Population,`Electric_power_consumption_(kWh_per_capita)`))+geom_point(color="red")+geom_line(aes(y = Estimated_values,),color="blue",linetype="dashed")
```

```{r}
ggplot(electric_omitted,aes(`Total Industries`,`Electric_power_consumption_(kWh_per_capita)`))+geom_point(color="red")+geom_line(aes(y=Estimated_values))
```


# Normalizing the data for Model 4.1

```{r}
sqr_Urban_Population_scale=scale(sqr_Urban_Population)
electric_omitted_scaled=na.omit(scale(electric))
electric_omitted_scaled=data.frame(electric_omitted_scaled)
model4.2=lm(electric_omitted_scaled$Electric_power_consumption_.kWh_per_capita.~sqr_Urban_Population_scale+electric_omitted_scaled$Total.Industries)
summary(model4.2)

```

# Predicting 

```{r}
# For un-scaled Model 4.1
electric_est=read_excel("Compiled.xlsx",sheet = "Estimation")
electric_est=electric_est[-1:-30,]
m=-7.640+0.000000000000002549*(electric_est$Urban_Population^2)+0.001426*(electric_est$`Total Industries`)
electric_est$Estimated_consumption=m
tail(electric_est$Estimated_consumption)
```

# Visualization


```{r}
ggplot(electric_est,aes(Urban_Population,`Electric_power_consumption_(kWh_per_capita)`))+geom_point(color="red")+geom_line(aes(y = electric_est$Estimated_consumption,),color="blue",linetype="dashed")
```

- From the above diagram we can see the projected value for power consumption till 2050.



# Generation of Energy

```{r}
m
gen_energy=read_excel("Compiled.xlsx",sheet = "Sheet3")
gen_energy_omit=na.omit(gen_energy)
cor(gen_energy_omit$`Total_Electricity_Renewable(kWh)`,gen_energy_omit$Estimated_consumption)
plot(gen_energy_omit$Estimated_consumption,gen_energy_omit$`Total_Electricity_Renewable(kWh)`)
```

# Regression Model

```{r}
gen_model1=lm(gen_energy_omit$`Total_Electricity_Renewable(kWh)`~gen_energy_omit$Estimated_consumption)
summary(gen_model1)
```

```{r}
gen_model2=lm(gen_energy_omit$`Total_Electricity_Renewable(kWh)`~log(gen_energy_omit$Estimated_consumption))
summary(gen_model2)
```

```{r}
acf(gen_model2$residuals)
dwtest(gen_model2)
bgtest(gen_model2,order = 1,type = "Chisq")
```


# Prediction Generation

```{r}
p=-10900000000+57660000*(gen_energy$Estimated_consumption)
gen_energy$predicted_generation=p
p
```




#Visualizing the estimated generation of Renewable energy

```{r}
ggplot(gen_energy_omit,aes(`Total_Electricity_Renewable(kWh)`,Estimated_consumption))+geom_point(color="red")+geom_line(aes(y = Estimated_consumption,),color="blue",linetype="dashed")
```


```{r}
Comparison=read_excel("Compiled.xlsx",sheet = "Sheet3")
total_consumption=Comparison$Estimated_consumption*Comparison$Population_total
total_renewable_generation=p
Final=cbind(Comparison$Year,total_consumption,total_renewable_generation)
Final=data.frame(Final)
head(Final)
```

# Visualization

```{r}
ggplot(gen_energy_omit,aes(`Total_Electricity_Renewable(kWh)`,Estimated_consumption))+geom_point(color="red")+geom_line(aes(y = Estimated_consumption,),color="blue",linetype="dashed")
```


```{r}
plot(Final$V1,Final$total_consumption,type="l",col="red")
abline(lm(Final$V1~Final$total_renewable_generation),col = "green")

```

```{r}
Final$total_renewable_generation
```









